\begin{abstract}
\textit{Smart contracts as computer code which reside on blockchain, are receiving great attention in new business application 
because they allow parties to represent contract terms in program code and
thus eliminate the need for a trusted third party.
The creation process of writing valid, transparent contracts is difficult task.
Blockchain as distributed ledger technology is increasingly used as transnational data storage between parties and it gains good popularity among new industries in last few years. Blockchain implemented in different areas of applications such as social, healthcare, logistic and etc. It is also capable to execute smart contract and prevents data tampering by validating transaction through consensus protocol. 
Research on this topic is still on early stage in science. Since our goal is to analysis the way of integrating semantic web licensing using DALICC library and deploying smart contract, we divide this research 
into four sections: first we focused on how smart contract build up on blockchain. Second, we demonstrate how blockchain can integrate with semantic web technology. It is focused on some solutions for indexing and executing smart contract on Ethereum blockchain. And third section, It is focused on Data Licenses Clearance Center (DALICC) as a framework helps to detect license conflict and reduce the costs of rights clearance. And in the last section, we present project to present all these topics in the form of DApp.}

 



\end{abstract}