\section{Introduction}

Etherem is one of the most popular blockchain platform which capable to generate decentralized application using smart contract. Ethereum is well-known for managing cryptocurrency using smart contract to automate this transaction.
It has been the best platform for developer coding smart contract in decentralized paradigm to generate decentralized application DApp.\\
Ethereum can be used in different scenarios, one strategy is to extract data from its blockchain network, linking  this data with the datasets of traditional web and query on them to generate new insight. \\
Another idea is, using semantic wen to standardize model and integrate data on web.  \textit{Tim Berners-Lee} described semantic web as model to extend web and allows to integrate machine with human. \\
Using semantic web enable access, integration and query on data sources, and create verity insight between different application domains. It uses ontology to allow query from the web using SPARQL and linking datasets. \\
Ontologies represent ethereum entities lick blocks, transaction message using RDF and Web Ontology Language(OWL). EthOn ontology formalize the concepts of ethereum blockchain on OWL, describing the ethereum objects as classes, data properties in ontology.\\
This thesis, we focused at two perposes: One ine to integrate semantic licenses from DALICC with smart contract. The other is to represent semantic model of deployed smart contracts. \\
This thesis present our efforts to build DApp to deploy smart contract in the presence of semantic licenses from DALICC, attaching licenses to contents, then applying semantic web techniques to link extracted date from ethereum transaction to semantic concepts adapted from Ethon ontology. \\
In the first chapter, we describe distributed ledger technology, blockchain, ethereum and some more details  to have better insight of used technology. In the next chapter, we represent some works around how semantic web can be applicable on blockcain. And on the last chapter, we present DApp to show smart contract integration with DALLICC semantic licences library and sementifying this deployment.




DALICC stands for Data Licenses Clearance Center is a framework that supports automated clearance of rights to help detecting license conflict and reduce the cost of high transaction related to manually clearance of licensing contents.
DALICC will develop and  integrate different functionalities that allows the automated clearance of rights issues.\\
In this thesis, deals with two things: One is the problem of linking license to contents for this purpose, we use Therefore, this work aims to find an appropriate and
generic method to attach semantic licenses to data and content. To achieve this, an
approach with a blockchain was chosen to design the entire system in a decentralized
and therefore trustworthy manner. Specifically, the Ethereum Platform was chosen,
because it is one of the most popular platforms for decentralized applications in the\\
Smart contract is computer program that expressed the content of agreements and preform transaction on blockchain when specific conditions are met. Smart contract preform verified transaction on blockhain without third party or any supervisors, thus ensuring us to transparent, valid and secure transaction.
AS Blockchain as distributed ledger become much popular and widely used in many field, the need of making query of such data becomes more important.
As blockain is distributed ledger which store data and transactions, querying them becomes challenges task. This due to the fact that blockchian can allow transaction and payment without needing intermediary.
Moreover there is need to integrate blockchin with semantic web service, thus making use of some linked data tools to index blocks and transaction according to Ethereum ontology.  \\
